---
title: "Unit 4 Assignment Census"
author: "Vinyas"
date: "16 May 2016"
output: html_document
---
####Load data and split into training and test set
```{r load}
library(caTools)
library(rpart)
library(rpart.plot)
census=read.csv("Data Files/census.csv")
set.seed(2000)
split=sample.split(census$over50k,SplitRatio = 0.6)
censustrain=subset(census,split==T)
censustest=subset(census,split==F)
```

#####Build a logistic regression model to predict the dependent variable "over50k", using all of the other variables in the dataset as independent variables. Use the training set to build the model

#####Which variables are significant, or have factors that are significant? 
```{r glm}
censusglm=glm(over50k~.,data = censustrain,family = "binomial")
summary(censusglm)
```

#####What is the accuracy of the model on the testing set? Use a threshold of 0.5. 
```{r 1.2}
predict_census=predict(censusglm,newdata=censustest, type = "response")
sum(diag(table(censustest$over50k,predict_census>0.5)))/nrow(censustest)
sum(table(censustest$over50k,predict_census>0.5)[1,])/nrow(censustest)

```

#####What is the area-under-the-curve (AUC) for this model on the test set?
```{r 1.4}
library(ROCR)
ROCRpred=prediction(predict_census,censustest$over50k)
as.numeric(performance(ROCRpred,"auc")@y.values)
```

#####Build a classification tree to predict "over50k"
```{r 2.1}
census_cart=rpart(over50k~.,data=censustrain,method = "class")
prp(census_cart)
```

```{r 2.3}
predcart=predict(census_cart,newdata=censustest,type="class")
table(censustest$over50k,predcart)
sum(diag(table(censustest$over50k,predcart)))/nrow(censustest) 
#Accuracy

predict_census3=predict(census_cart,newdata=censustest)
ROCRpred3=prediction(predict_census3[,2],censustest$over50k)
as.numeric(performance(ROCRpred3,"auc")@y.values) #AUC
```


