---
title: "Unit 4 D2Hawkeye"
author: "Vinyas"
date: "14 May 2016"
output: 
  html_document: 
    fig_caption: yes
    theme: spacelab
---

```{r load}

claims=read.csv("Data Files/ClaimsData.csv")
summary(claims)
str(claims)
```

#####percentage of people in each bucket in 2009
```{r buckets}
table(claims$bucket2009)*100/nrow(claims)  
```

#####Splitting the data
```{r splitting}
library(caTools)
set.seed(88)
spl=sample.split(claims$bucket2009,SplitRatio = 0.6 )
claimstrain=subset(claims,spl==T)
claimstest=subset(claims,spl==F)
```

#####Average age and proportion of people in the training set had at least one diagnosis code for diabetes

```{r q1}
mean(claimstrain$age)
table(claimstrain$diabetes==1)/nrow(claimstrain)
```

#####Accuracy of baseline test
```{r baseline}
sum(diag(table(claimstest$bucket2009,claimstest$bucket2008)))/nrow(claimstest)

#Sum of all the diagonal elements divided by number of observations in claimstest
```

#####Penalty Matrix

```{r penalty_matrix}
PenaltyMatrix = matrix(c(0,1,2,3,4,2,0,1,2,3,4,2,0,1,2,6,4,2,0,1,8,6,4,2,0), byrow=TRUE, nrow=5)

PenaltyMatrix
```

#####Penalty error of baseline matrix
```{r baseline_error}

as.matrix(table(claimstest$bucket2009, claimstest$bucket2008))*PenaltyMatrix

sum(as.matrix(table(claimstest$bucket2009,claimstest$bucket2008))*PenaltyMatrix)/nrow(claimstest)

```

If we used the baseline method of predicting the most frequent outcome for all observations. This new baseline method would predict cost bucket 1 for everyone.

1. What would the accuracy of this baseline method be on the test set?
2. What would the penalty error of this baseline method be on the test set?

```{r q2}
table(claimstest$bucket2009)[1]/nrow(claimstest)

sum(as.matrix(table(claimstest$bucket2009))*as.matrix(c(0,2,4,6,8),byrow=TRUE,nrow=1))/nrow(claimstest)

```

#####Load library rpart and rpart.plot
```{r rpart}
library(rpart)
library(rpart.plot)
```

#####Build a CART model

```{r model}
ClaimsTree = rpart(bucket2009 ~ .-reimbursement2009, data=claimstrain, method="class", cp=0.00005)
#All variables except reimbursement2009

prp(ClaimsTree)
```

#####Prediction
```{r predict}

 PredictTest = predict(ClaimsTree, newdata = claimstest, type = "class")

 table(claimstest$bucket2009, PredictTest)
 
 sum(diag(table(claimstest$bucket2009,PredictTest)))/nrow(claimstest)
 #Accuracy
 
```
 
#####Penalty error 
```{r penalty_error} 
 as.matrix(table(claimstest$bucket2009, PredictTest))*PenaltyMatrix

sum(as.matrix(table(claimstest$bucket2009,PredictTest))*PenaltyMatrix)/nrow(claimstest)
#Penalty Error

```
#####New model with paramaters set to minimize the penalty error ie loss matrix

```{r model2}
ClaimsTree = rpart(bucket2009 ~ .-reimbursement2009, data=claimstrain, method="class", cp=0.00005,parms=list(loss=PenaltyMatrix))
```


##### Redo predictions 
```{r predict2}
PredictTest = predict(ClaimsTree, newdata = claimstest, type = "class")

table(claimstest$bucket2009, PredictTest)

#Accuracy
sum(diag(table(claimstest$bucket2009,PredictTest)))/nrow(claimstest)
```

#####New penalty error
```{r penalty_error2}

sum(as.matrix(table(claimstest$bucket2009, PredictTest))*PenaltyMatrix)/nrow(claimstest)
```
